Online Verification of Commutativity

### 2020-10-07 acmPaper/paper.tex
algorithm captions

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
% \documentclass[sigplan,nonacm=true]{acmart}
\documentclass[sigplan]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    S $\gets$ existingGraph.extractReachableSection(v)\;
    T $\gets$ createMinimumSpanningTree(S)\;
    excludedEdges = edges in subgraph S - edges in T\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = T.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement((firstPath, e))\;
    } 
}
\KwRet{$R_s$}\;

\caption{Finding a spanning set of path pairs.}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Finding a minimal spanning set.}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Na\"{i}ve baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\caption{Computation time for 9-node graph of density 0.4, averaged over ten runs.}
\label{tab:times} %TODO debug and fix label not working.
\end{table}

@@

\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Na\"{i}ve baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    ~\ref{algo_online_polynomial} & 78.3 \\
    ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\caption{Output size for 9 node graph of density 0.4, averaged over ten runs}
\label{tab:sizes}
\end{table}

>>>>

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
% \documentclass[sigplan,nonacm=true]{acmart}
\documentclass[sigplan]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{microtype}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

Graph existingGraph\;
$R_s$ $\gets$ \{\}\;
\ForEach{node v in V}{
    Subgraph $\gets$ existingGraph.extractReachableSection(v)\;
    Tree $\gets$ createMinimumSpanningTree(Subgraph)\;
    excludedEdges = edges in Subgraph - edges in Tree\;
    \ForEach{edge e $\in$ excludedEdges}{
        firstPath = Tree.findPath(source: e.source, sink: e.sink)\;
        $R_s$.addElement((firstPath, e))\;
    } 
}
\KwRet{$R_s$}\;

\caption{Finding a spanning set of path pairs, as in section ~\ref{sec:batchBaseline}}\label{algo_spanning_set}
\end{algorithm}

@@

\caption{Finding a minimal spanning set, as described in section ~\ref{sec:batchBaseline}}\label{algo_minimal_spanning_set}
\end{algorithm}

@@

\begin{table}
    \caption{Computation time for 9-node graph of density 0.4, averaged over ten runs.}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Na\"{i}ve baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\label{tab:times} %TODO debug and fix label not working.
\end{table}

@@

\begin{table}
    \caption{Output size for 9 node graph of density 0.4, averaged over ten runs}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Na\"{i}ve baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    ~\ref{algo_online_polynomial} & 78.3 \\
    ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\label{tab:sizes}
\end{table}
